MSB1015_Assignment 2

### 2019-10-13 MSB1015_Assignment2_SuzannetenHage.Rmd
Added documentation in section 5
Documentation of plsr, RMSEP and predict functions in section 5 was missing.

>>>>

The plsr function trains several models with different numbers of components. As plsr is used here, it determines the number of components by itself (and will generally use 1 up to (descriptors - 1) components). It also possible to fix the number of components by using the ncomp = value argument.

RSMEP will calculate the error for each model built by plsr and therefore, error_PLS will contain a vector containing the error for each number of components (see section 6 for visualization of this).

The function predict will predict the boiling points based on each mode in PLS_model.
